---
format: gfm
---

<!-- README.md is generated from README.Qmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# targets-uahpc

⚠️ Work in progress ⚠️

<!-- badges: start -->
<!-- badges: end -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This is a minimal example of a [`targets`](https://docs.ropensci.org/targets/) workflow that can be run on your computer or on the University of Arizona cluster computer through [Open on Demand](https://ood.hpc.arizona.edu/).  `targets` is an R package for workflow management that can save you time by automatically skipping code that doesn't need to be re-run when you make changes to your data or code.  It also makes parallelization relatively easy.

## Prerequisites:

- A UAz HPC account
- Some familiarity with R, RStudio, and the `targets` package
- A GitHub account

## To Use:

1. SSH into the UA HPC
2. Start an interactive sesssion, e.g. with `elgato && interactive -a <username>`
3. Clone this repo `git clone https://github.com/cct-datascience/targets-uahpc.git`
4. Load R with `module load R`
5. Launch R from within the `targets-uahpc/` directory with `R`
6. `renv` should install itself.  After it is done, you can install all necessary R packages with `renv::restore()`
7. Customize the controller....
8. Run `tar_make()`